---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "")
```

# VECM

[![Status](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Version](https://img.shields.io/badge/version-0.1-orange.svg)]()
[![CRAN](https://www.R-pkg.org/badges/version/VECM)](https://CRAN.R-project.org/package=VECM)
[![License](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://choosealicense.com/licenses/gpl-3.0)

## Overview

The **VECM** package provides tools for estimating and analyzing multivariate time series data that exhibit long-term equilibrium relationships, allowing for the incorporation of both short-term dynamics and long-run cointegration between variables. It facilitates model specification, estimation, impulse response analysis, and forecasting. 

The package is on development and further features will be introduced in future versions.

## Installation

**VECM** is not on [CRAN](https://CRAN.R-project.org) yet, but you can install it as follows:

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("GianlucaCarpigo/VECM")
```

$\underline{\text{Attention!}}$ Windows users must have [Rtools](https://CRAN.R-project.org/bin/windows/Rtools) installed for this to work.

## Meta

**VECM** is licensed under the [GNU General Public License Version 3](LICENSE.md).

To help develop the package, please follow the [contribution guidelines](/.github/CONTRIBUTING.md).

If you have any questions, you can ask them in the [discussion forum](https://github.com/GianlucaCarpigo/VECM/discussions).

## Code of conduct

**VECM** is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By contributing, you agree to abide by its terms.
